\large{Vipassana for Hackers} \\ \Huge{Paper Two: The Brain} \\ \large\textit{Version 0.2}

### 2019-10-07 paper-two/paper-two.tex
cleaning up jpgs

The Inferior Parietal lobe (IPL) is situated in the back of the brain and it is
involved in the perception of facial stimuli. \cite{ipl}
The IPL has been hypothesized as being involved in distinguishing self from others, 
in a study where subjects were asked to retrieve 
previous judgments about oneself, their friend and the Dutch queen, 
the activation of the IPL was seen to decrease with decreasing self-reference. \cite{iplself} 
Another study also used Transcranial Magnetic Stimulation (TMS) to create a sort of "virtual lesion" 
(transiently disturb the neural circuitry in that area) of
the right-IPL and showed that this disrupts self-other discrimination. \cite{ipltms}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=5cm]{images/fmri-dmn.jpg}
  \caption{fMRI scan of the Default Mode Network.}
  \label{fig:fmri-dmn}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=5cm]{images/fmri-cen.jpg}
  \caption{fMRI scan of the Central Executive Network.}
  \label{fig:fmri-cen}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=5cm]{images/fmri-sn.jpg}
  \caption{fMRI scan of the Salience Network.}
  \label{fig:fmri-sn}
\end{figure}

@@

\bibitem{iplself}
 Hans C. Lou, Bruce Luber, Michael Crupain, Julian P. Keenan, Markus Nowak, 
 Troels W. Kjaer, Harold A. Sackeim, Sarah H. Lisanby
 \textit{Parietal cortex and representation of the mental Self}
  Proc Natl Acad Sci U S A. 2004 Apr 27; 101(17): 6827–6832.

\bibitem{ipltms}
 Lucina Q. Uddin, Istvan Molnar-Szakacs, Eran Zaidel, Marco Iacoboni
 \textit {rTMS to the right inferior parietal lobule disrupts self–other discrimination}
  Social Cognitive and Affective Neuroscience, Volume 1, Issue 1, June 2006, 
  Pages 65–71, https://doi.org/10.1093/scan/nsl003

>>>>

The Inferior Parietal lobe (IPL) is situated in the back of the brain and it is
involved in the perception of facial stimuli. \cite{ipl}

\todo{Expand on IPL: How does the IPL contribute to our sense of self?}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=5cm]{images/fmri-dmn.png}
  \caption{fMRI scan of the Default Mode Network.}
  \label{fig:fmri-dmn}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=5cm]{images/fmri-cen.png}
  \caption{fMRI scan of the Central Executive Network.}
  \label{fig:fmri-cen}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=5cm]{images/fmri-sn.png}
  \caption{fMRI scan of the Salience Network.}
  \label{fig:fmri-sn}
\end{figure}

@@
